%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[sfdefault]{libertine}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \vspace{-3pt}
      \textbf{#1} & #2  \\
      \textit{\footnotesize#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 &
    \footnotesize#2 \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ryan Batubara} \\ \vspace{2pt}
    \small 657-543-6822 $|$ \href{mailto:ryan.y.batubara@gmail.com}{\underline{ryan.y.batubara@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/ryan-batubara/}{\underline{linkedin.com/in/ryan-batubara}} $|$
    \href{https://github.com/rybplayer}{\underline{github.com/rybplayer}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA}
      {Mathematics-Computer Science, Data Science Double Major}{Sep. 2022 -- June 2026}
      \resumeItemListStart
        \resumeItem{Coursework: Machine Learning, Recommender Systems, Databases, Linear Algebra, Data Structures, Optimization, Algorithms, Graph Theory, Abstract Algebra, Analysis, Statistics, Quantum Computing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mathematics Undergraduate Researcher}{January 2024 -- Present}
      {\href{https://github.com/UCSD-computational-number-theory/GPUFiniteFieldMatrices.jl}{https://github.com/UCSD-computational-number-theory/GPUFiniteFieldMatrices.jl}}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Optimized Artin-Mazur height, toric controlled reduction runtimes by 50x using Julia and CUDA on the GPU.}
        \resumeItem{Developed multiple open-source Julia packages for fast GPU linear algebra beating FLINT using CUDA.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{September 2025 -- Present}
      {Merah Putih Ltd.}{Jakarta, Indonesia (Remote)}
      \resumeItemListStart
        \resumeItem{Created web dashboard from scratch for 20 management systems with React, Tailwind, TypeScript, and Leaflet.}
        \resumeItem{Tested and deployed 10 websites for performance and mobile compatibility using AWS, Vitest, Playwright.}
    \resumeItemListEnd

    \resumeSubheading
      {Data Science Undergraduate Researcher}{September 2024 -- June 2025}
      {\href{https://datadiv.wordpress.com/about-us/}{https://datadiv.wordpress.com/about-us/}}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Worked with Smarr Lab and formerly incarcerated people to explore data on incarceration vs. social policies.}
        \resumeItem{Gathered GBs of data from US government to visualize and analyse incarceration trends using Python and SQL.}
    \resumeItemListEnd

    \resumeSubheading
      {AI Research Intern}{July 2025 -- September 2025}
      {\href{https://gani.ai}{https://gani.ai}}{Jakarta, Indonesia (Remote)}
      \resumeItemListStart
        \resumeItem{Reduced model costs 10x by implementing in-house LLM pipeline with LangChain and AWS SageMaker.}
        \resumeItem{Finetuned large language models for legal and due diligence generation using RAG, QLoRA, and Unsloth.}
    \resumeItemListEnd

    \resumeSubheading
      {CSE PACE Mentor}{Sept 2023 -- Present}
      {\href{https://pace.ucsd.edu/}{https://pace.ucsd.edu/}}{San Diego, CA}
      \resumeItemListStart
        \resumeItem{Onboarded 100s of first-year CS students weekly on cutting-edge CS topics and academic resources.}
        \resumeItem{Worked alongside educational researchers on novel pedagogy for incoming CS students, such as \href{https://dl.acm.org/doi/pdf/10.1145/3626252.3630964}{\underline{this paper}}.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{AirBnB Listing Success Predictor} $|$ \emph{Python, Pandas, TensorFlow} $|$ \footnotesize\href{https://rybplayer.github.io/AirBnB-Predictor/}{https://rybplayer.github.io/AirBnB-Predictor/}}{}
        \resumeItemListStart
        \resumeItem{Created website with 10s of visuals using Plotly to communicate the key features of successful AirBnB listings.}
        \resumeItem{Used TensorFlow, SciKit-Learn to implement RNN, CNN machine learning to predict review scores at 0.17 MAE.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Step Counting Algorithm Visualization} $|$ \emph{Javascript, D3.js} $|$ \footnotesize\href{https://rybplayer.github.io/StepCounterVisualization/}{https://rybplayer.github.io/StepCounterVisualization/}}{}
        \resumeItemListStart
        \resumeItem{Made website with 10s of visuals using D3.js and Javascript to interactively visualize step counting algorithms.}
        \resumeItem{Used Python to process 100 hours of accelerometer data to evaluate various step counting algorithms.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{UCSD Class Scraper and Plotter} $|$ \emph{Python, Rust, Javascript} $|$ \footnotesize\href{https://github.com/UCSD-Historical-Enrollment-Data/}{https://github.com/UCSD-Historical-Enrollment-Data/}}{}
        \resumeItemListStart
        \resumeItem{Scraped and plotted 40000 UCSD classes/hour in parallel with Rust, Javascript, Python on Digital Ocean.}
        \resumeItem{Condensed 100GBs of scraped data into meaningful matplotlib plots for over 10,000 UCSD students.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Data Science}{: 
    ScikitLearn, PyTorch, TensorFlow, AWS SageMaker, Pandas, Numpy, D3.js, Plotly, Matplotlib, Seaborn
    } \\
    \textbf{Developer Tools}{: 
    Git, Docker, Kubernetes, Digital Ocean, Github, Tmux, Jupyter, Swagger, Postman, Bun, Vitest
    } \\
    \textbf{Frameworks and Libraries}{: 
    React, Next.js, Qiskit, Oscar, Flint, Selenium, CUBLAS, Unsloth, LangChain, CUDA, Vite
    } \\
    \textbf{Hobbies}{: 
    Classical Guitar, Puzzles, PC Building, Video Games
    } \\
    \textbf{Languages}{: 
    Python, Julia, SQL, Javascript, Typescript, C, C++, ARM, Java, R, Rust, MATLAB, LaTeX, Bash, Powershell
    } \\
    }}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}l}
        SDSU Big Data Hackaton Best Geospatial Thinker, 2024 & 
            \footnotesize\href{https://bigdataforsandiego.github.io/}{https://bigdataforsandiego.github.io/} \\
        World Mathematics Invitational Bronze, \emph{Fukuoka, Japan}, 2019 & 
            \footnotesize\href{https://www.wminv.org/Subpage/Winners_2019.aspx}{https://www.wminv.org/Subpage/Winners\_2019.aspx} \\
        World Mathematics Invitational Bronze, \emph{Seoul, Korea}, 2018 & 
            \footnotesize\href{https://www.wminv.org/Subpage/Winners_2018.aspx}{https://www.wminv.org/Subpage/Winners\_2018.aspx} \\
      \end{tabular*}\vspace{-10pt}
    }}
    
\end{itemize}

%-------------------------------------------
\end{document}
